Report and Figures

### 2016-11-11 figs.Rmd
more grids, multigroup
labelled detroit

cities <- c('Philadelphia', 'Atlanta')

@@

@@

>>>>

cities <- c('Philadelphia', 'Atlanta', 'Chicago', 'Detroit')

tab <- data.frame(city = character(), H_Y = numeric(), I_XY = numeric(), J_XY = numeric())

@@

  columns = races
  stuff <- compx::info_analysis(tracts, columns = columns, resolution = NULL, grid_tract = grid_tract, grid = grid)

@@

  new_row <- data.frame(city = city, H_Y = stuff$H_Y, I_XY = stuff$I_XY, J_XY = stuff$J_XY)
  tab <- rbind(tab, new_row)
}
